processing

### 2022-03-30 code/processing_code/processing_code.Rmd
adding results
volunteer data and CV

#merging mutated data
cleansampledata <- full_join(otherdata, julydata) %>% select(-"id",
                                                         -"id2",
                                                         -"rep_particles_l",
                                                         -"a_count",
                                                         -"b_count", 
                                                         -"c_count",
                                                         -"d_count",
                                                         -"volume_ml",
                                                         -"obs_type")

@@

# location to save file
save_data_location <- here::here("data","processed_data","cleansampledata.rds") 
save_data_location1 <- here::here("data","processed_data","volunteer.rds") #saving july volunteer data to look at later
save_data_location2 <- here::here("data","processed_data","controldata.rds")

saveRDS(cleansampledata, file = save_data_location)
saveRDS(volunteer, file = save_data_location1)
saveRDS(controldata, file = save_data_location2)

>>>>

#merging mutated data
fullsampledata <- full_join(otherdata, julydata) # to preserve a and b counts
cleansampledata <- fullsampledata %>% select(-"id",
                                                         -"id2",
                                                         -"rep_particles_l",
                                                         -"a_count",
                                                         -"b_count", 
                                                         -"c_count",
                                                         -"d_count",
                                                         -"volume_ml",
                                                         -"obs_type")

@@

# location to save file
save_data_location <- here::here("data","processed_data","cleansampledata.rds") 
save_data_location1 <- here::here("data","processed_data","volunteer.rds") #saving july volunteer data to look at later
save_data_location2 <- here::here("data","processed_data","controldata.rds")
save_data_location3 <- here::here("data", "processed_data", "fullsampledata.rds")

saveRDS(cleansampledata, file = save_data_location)
saveRDS(volunteer, file = save_data_location1)
saveRDS(controldata, file = save_data_location2)
saveRDS(fullsampledata, file = save_data_location3)
